### 2017-12-11 Draft2/Bibliography.tex
Take care of the bib!

\begin{thebibliography}{9}

\bibitem{ceillog2}
	Ko, James L. "Algorithm for implementing ceiling of log 2." \textit{GitHub}, 12 Nov. 2017,\\ \texttt{https://github.com/jamesqo/StsProject/blob/master/src/StsProject/Internal/MathHelpers.cs}
\end{thebibliography}

>>>>

\begin{flushleft}
\begin{thebibliography}{9}

\bibitem{tildedef}
	de Bruijn, Nicolaas G. \textit{Asymptotic Methods in Analysis}. Dover Publications, 1981.

\bibitem{littleodef}
	Cormen et al. \textit{Introduction to Algorithms, Second Edition}. The MIT Press, 2001.

\bibitem{amortized}
	Fiebrink, Rebecca. \textit{Amortized Analysis Explained}. Princeton University, 2007. Available at \texttt{https://www.cs.princeton.edu/~fiebrink/423/AmortizedAnalysisExplained\_Fiebrink.pdf}.

\bibitem{fptables}
	Fog, Agner. \textit{Lists of instruction latencies, throughputs and micro-operation breakdowns for Intel, AMD and VIA CPUs}. Technical University of Denmark, 2017. Available at \texttt{http://www.agner.org/optimize/instruction\_tables.pdf}.

\bibitem{ceillog2}
	Leiserson et al. \textit{Using de Bruijn sequences to Index a 1 in a Computer Word}. MIT Laboratory for Computer Science, 1998. Available at \texttt{http://supertech.csail.mit.edu/papers/debruijn.pdf}.

\end{thebibliography}
\end{flushleft}

### 2017-12-11 Draft2/Indexing.Growth.tex
Take care of the bib!

At first glance, $\FuncDecompose$ appears to be expensive: logarithms and exponentiation normally imply use of floating-point instructions, which tend to be slower than integer-based ones. However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.

To see this, note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. Using the concept of de Bruijn sequences, one can index the leftmost $1$ in the binary representation of $i$ in constant time \cite{ceillog2}. (For example, if $i = 9 = 1001\text{ in binary}$, the index of the leftmost $1$ starting from the right is $3$.) This index is the same as $\left\lfloor \log_2 i \right\rfloor$. Using the fact that $\left\lceil \log_2 (i + 1) \right\rceil = \left\lfloor \log_2 i \right\rfloor + 1$ (as there cannot be natural numbers between $\log_2 i$ and $\log_2 (i + 1)$), one can easily find $\VarIndexBuffer$. Finally, calculating $\VarGrowthFactor^{\VarIndexBuffer - 1}$ becomes a simple bit shift when $\VarGrowthFactor = 2$.

>>>>

At first glance, $\FuncDecompose$ appears to be expensive: logarithms and exponentiation normally imply use of floating-point instructions, which tend to be slower than integer-based ones \cite{fptables}. However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.

To see this, note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. Using the concept of de Bruijn sequences, one can index the leftmost $1$ in the binary representation of $i$ in constant time \cite{ceillog2}. (For example, if $i = 9 = 1001\text{ in binary}$, the index of the leftmost $1$ starting from the right is $3$.) This index is the same as $\left\lfloor \log_2 i \right\rfloor$. Using the fact that $\left\lceil \log_2 (i + 1) \right\rceil = \left\lfloor \log_2 i \right\rfloor + 1$ (as there cannot be natural numbers between $\log_2 i$ and $\log_2 (i + 1)$), one can easily find $\VarIndexBuffer$. Finally, calculating $\VarGrowthFactor^{\VarIndexBuffer - 1}$ to find $\VarIndexElement$ becomes a simple bit shift when $\VarGrowthFactor = 2$.
